\chapter{Introduction}
	
		\section{Project overview}
		
			The goal of this project is to design and implement the software 
			behind an online auction website such as eBay. The codename of our project 
			is {\emph Salesmen}. 

			This project is embedded in the Software Engineering course, 
			which is designed for senior students of Computer Science and Engineering 
			at the Vrije Universiteit Brussel. It has a threefold purpose:
			
			\begin{enumerate}
				\item Get familiar with the software development process and learn to work
				in a team.
				
				\item Develop a system that supports the functionality of an auction website. 
				This means that a user will be able to sell or buy items in an online auction. 
				
				\item Develop and maintain a general website on our project. Up to date 
				versions of all documents such as minutes, timesheets and deliverables will be 
				available at any time. This site will be hosted at
				\url{http://wilma.vub.ac.be/~se2_0910/}.
			\end{enumerate}	
			
			The software of the application will be written in Java and 
			distributed under an Open Source license.	
		
		\section{Project deliverables}
		
		\begin{itemize}
			
			\item Software documentation (see \ref{deadlines})
			\item Minutes: 3 days after meeting
			\item Timesheets: every Monday before 12H00
			\item Source code
			
		\end{itemize}	
		
		All of those documents will be available written in English on our website.
	
		
		\section{Reference materials}
		
			\begin{itemize}
			
				\item 
					\url{http://tinf2.vub.ac.be/~dvermeir/courses/software_engineering/slides.pdf}
			
				\item Eric J. Braude, \emph{Software Engineering -
				An Object-Oriented Perspective}, John Wiley \& Sons, 2001. ISBN 0-471-32208-3.
			
			\end{itemize}
			
		\section{Definitions and acronyms}

			\begin{tabular}{l l}

				\textbf{SCMP} & Software Configuration Management Plan \\
				\textbf{SDD} & Software Design Plan \\
				\textbf{SPMP} & Software Project Management Plan \\
				\textbf{SQAP} & Software Quality Assurance Plan \\
				\textbf{SRS} & Software Requirements Specification \\
				\textbf{STD} & Software Test Document \\
				\textbf{COCOMO} & Constructive Cost Model

			\end{tabular}				
		
		\section{Revision history}
		
			\begin{tabular}{l l l l}
				\\
				\FL Version & Date & Name & Description
				\ML 0.1 & 21/10/09 & Nick De Cooman & Initial draft
				\NN 0.2 & 22/10/09 & Nick De Cooman & Revision after quality control
				\NN 1.0 & 12/11/09 & Nick De Cooman & Revision including customer's comments
				\NN 1.1 & 20/11/09 & Nick De Cooman & Adding estimation of costs
				\\
			\end{tabular}	
		
		