\chapter{Work packages, schedule and budget}
			
			\section{Costs}
			
			\subsection{Estimation}
			
			To calculate an estimation of costs, the COCOMO algorithm developed by Barry Boehm
			will be used. Depending on the number of lines of code, the costs and efforts of this
			project can be computed. Off course, this is just an estimation and will differ from
			reality. The algorithm provides next formulas in order to calculate the effort and
			cost:
			
			\begin{center}
			Effort Applied: $ E = a \cdot (KLOC)^{b} $ \\
			Development Time: $ D = c \cdot E^{d} $ \\
			People required: $ P = \frac{E}{D} $ \\
			\end{center}
			
			KLOC is the estimation of the code length expressed in thousands of lines of code.
			Our project can be classified as a semi-detached project which means that our team of
			a medium size has a mixed experience working with a mix of rigid and less than rigid
			requirements. Therefore, the parameters a, b, c, d are defined as in table \ref{par}. 		
			
			
			\begin{table}
				\begin{center}
			\begin{tabular}{l l}
				\FL Parameter & Value
				\ML a & 3.0
				\NN b & 1.12
				\NN c & 2.5
				\NN d & 0.35
			\end{tabular}
				\end{center}
				\caption{COCOMO Parameters for a semi-detached project}
				\label{par}
			\end{table}	
			
			By analyzing simular projects, we estimate to write 10KLOC. This brings the total
			effort to:
			
			\begin{center}
				$ E = 3.0 \cdot 10^{1.12} \approx 39,55 $ man-months
			\end{center}
			
			The total development time thus becomes:
			
			\begin{center}
				$ D = 2,5 \cdot 39,55^{0,35} \approx 9,06 $ months
			\end{center}
			
			This results in a total staff estimation of
			
				\[ P = \frac{39,55 \textrm{ man-months}}{9,06 \textrm{ months}} \approx 4,37 \textrm{ people} \]
			
			Using the COCOMO algorithm, we can thus conclude that 4,37 people are needed to
			realise our project in 9,06 months. 
			
			In our case however, we can rely on 7 people. Assuming we will have 27 weeks in order
			to achieve our goals, and a month accounts 4,3 weeks, the total development time
			can be calculated as:
				\[ E = 7 \textrm{ people} \times \frac{27 \textrm{ weeks}}{4,3 \textrm{ weeks/months}} \approx 43,95 \textrm{ man-months} \] 
			
			This means that we have more time to realise the project than needed
			according to the estimation. 
			
			\subsection{Real costs}
			
			
			
			\section {Dependencies}
			
			At this time, it is only possible to provide 1 general dependency :
			
			\begin{itemize}
				
				\item Iteration 2 depends on the completion of iteration 1.
				
			\end{itemize}
			
			
			\section{Planning}	
				
			
			
			
	